Planar Maximal Covering with Ellipses

### 2019-04-28 quali/quali.presentation/slides.tex
remove unused
WIP

\usepackage{pgfplots}
\pgfplotsset{compat=1.4}
%\usepgfplotslibrary{external}
%\tikzexternalize

@@

	\begin{itemize}
		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$
		\item $D(q)$ is a unit disk with center at point $q$
		\item We will introduce an equivalent problem...
	\end{itemize}
\end{frame}

@@

		\caption{An instance of $MCD(\Pp,1)$.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
		%\fautor
		\label{fig:max_wieght_clique}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
	\begin{figure}[H]
		\centering

@@

@@

\begin{block}{Multiple disks}
	For every disk, try every possible assignment that the traversal goes through.
\end{block}

@@

	\begin{itemize}
		\item $E(q)$ is an axis-parallel ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
		\item Assuming unit weights for now
		\item Same algorithm for one disk
	\end{itemize}

@@

\begin{frame}{Cobertura Maximal por Ellipses}{$m$ elipses}
	content... algoritmo
\end{frame}

@@

\end{frame}
\end{document}

>>>>

\usepackage{pgfplots}
\pgfplotsset{compat=1.4}
\usepackage{algorithmicx}
\usepackage{algorithm}
%\usepgfplotslibrary{external}
%\tikzexternalize

@@

	\begin{itemize}
		\item $\Pp=\{p_1,\dots,p_n\}$ is the demand set with weights $w(p_i)>0$
		\item $w(A)$, $A\subset \Pp$, is the sum of weights of the points in $A$
		\item $D(q)$ is a unit disk with center at point $q$
		\item \cite{chazelle:1986} proposed a $\bigO(n^2)$ algorithm
		\item \cite{drezner} proposed a $\bigO(n^2\log{n})$ which our work is based on
		\item We will introduce an equivalent problem...
	\end{itemize}
\end{frame}

@@

		\caption{An instance of Maximum Weight Clique Problem.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
		%\fautor
		\label{fig:max_wieght_clique}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles (with respect to $D_i$) of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
	\begin{figure}[H]
		\centering

@@

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
\begin{figure}
	%\centering

	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
	\input{figures/mcd_sim.tex}
	%	\fautor
	%\label{fig:array_disks}
\end{figure}
\end{frame}

@@

\begin{block}{Multiple disks}
	For every disk, try every possible assignment that the traversal goes through. \cite{cabello:2006} proposed a $\bigO(n^{2m-1})$ algorithm.
\end{block}

@@

	\begin{itemize}
		\item $E(q)$ is an axis-parallel ellipse with center point $q$
		\item Assuming unit weights for now
		\item Same algorithm for one disk
	\end{itemize}

@@

\begin{frame}{Maximal Covering by Ellipses}
\begin{figure}[H]
	\centering

	\caption{Intersection points of $E_1$ with $E_2$ and $E_3$ along with opening and closing angles indicators.}
	\input{figures/3ellipses_with_gammas.tex}
	%	\fautor
	\label{fig:3ellipses_with_gammas}
\end{figure}
\end{frame}

\begin{frame}{Maximal Covering by Ellipses}{$m$ ellipses}
	Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by

	\begin{equation*}
	\max_{q_1, \dots, q_m}{\left|\bigcup_{i=1}^{m} \Pp \cap E_i(q_i)\right|},
	\end{equation*}

	\begin{itemize}
		\item $\E$ is a set of $m$ ellipses
		\item \cite{andreta,canbolat} are the works found on the problem which the ellipses have costs
		\item \cite{andreta} also developed a method for the non-axis-parallel case
	\end{itemize}
\end{frame}

\begin{frame}{Maximal Covering by Ellipses}{$m$ ellipses}
	\begin{algorithm}[H]
	%	\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
		%\KwIn{alskdjf}

		\begin{algorithmic}[1]
			\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and the shape parameters $(a, b)$ of an ellipse.}
			%\Ensure{A collection of subsets of $\Pp$ that the ellipse is able to cover.}

			%\item[]
			%\Procedure{$MCE_1$}{$\Pp, a, b$}
			%\State $Z \gets \{\}$ \Comment{A collection of subsets of $\Pp$, each being a possible coverage.}

			%\ForAll{$p_i \in \Pp$}
			%\State Let $E_i$ be the ellipse with center at $p_i$ and parameters $(a,b)$

			%\State Let $I_i$ be the set of ellipses that intersect with $E_i$

			%\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $E_i$}

			%\State $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$ %\Comment{The multiset of intersection angles with $E_i$.}

			%\ForAll{$j \in I_i$}
			%\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
			%\EndFor

			%\State $Z \gets Z \cup \{\{p_i\}\}$
			%\State $Cov \gets \{p_i\}$ \Comment{The set of active disks.}

			%\For{$cnt=1..2$} \Comment{Do it twice.}
			%\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
			%\State Let $p_a$ be the point represented by the ellipse that intersects $E_i$ at angle $a$. 
			%\If{$a$ is a starting angle}
			%\State $Cov \gets Cov \cup \{p_a\}$
			%\Else
			%\State $Cov \gets Cov \setminus \{p_a\}$
			%\EndIf
			%\State $Z \gets Z \cup \{Cov\}$
			%\EndFor
			%\EndFor
			%\EndFor

			%\State \Return $Z$
			%\EndProcedure

		\end{algorithmic}
	\end{algorithm}
\end{frame}

@@

\begin{frame}[allowframebreaks]
	\frametitle{References}
	\bibliographystyle{amsalpha}
	\bibliography{../references.bib}
\end{frame}

\end{document}
